Make any stupid plot you want

### 2021-01-20 draft/sections/math.tex
triangularization

We use fiber bundles\cite{FiberBundle2020, rowlandFiberBundle} to model data and graphics because they allow us to seperate the variables in a dataset from how the values  are connected to each other \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}.

@@

\subsubsection{Connectivity: Base Space $K$} 
\label{sec:data_base}
The fiber bundle is the gluing map $\pi$ between the fiber space included in the total space $E$ and the base space $K$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi"] & K
    \end{tikzcd}
\end{equation}

@@

Formally, $K$ is the quotient space \cite{QuotientSpaceTopology2020} of $E$, meaning it is the finest space such that every $k \in K$ has a corresponding fiber $F_k$ in $E$. In figure~\ref{fig:base_space_div}, $E$ is a rectangle divided by vertical fibers $F$, so the minimal $K$ for which there is always a mapping $\pi: F\rightarrow K$ is the straight line.

We encode indexing from $K$ to $E$ as sections $\tau$ of the fiber bundle that return corresponding records.

%%if we had a coordinate on

%%pull this down to triangulization section 
For example when $K$ has
\begin{align*}
    \textbf{vertexes}\;& \tau(k) \text{k= vertex id}\\
    \textbf{edges}\;& \tau(k,\alpha), \text{k = edge id, $\alpha$ = distance along edge} \\
    \textbf{faces}\;& \tau(k,\alpha_1, \alpha_2), \text{k = face id, $\alpha_1$ = x on face, $\alpha_2$ = y on face}
\end{align*}
such that we can check for continuity of sections $\tau$ by verifying that the edges align such that $\tau(k_{i},1) = \tau(k_{j},0)$.

@@

\subsubsection{Sample Qs}
In this section we formulate the minimal Q that will generate distinguishable graphical marks: non-overlapping scatter points, a non-infinitely thin line, and a simple heatmap.

@@

\subparagraph{Example}
\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{figures/math/triangle_torus.png}
    \label{fig:triangle_torus}
\end{figure}

Given data that lies on the toroidal space shown in figure~\ref{fig:triangle_torus}, the torus $K$ can be implemented as a simplacial complex of two 2-simplexes. We unfold the torus into the two triangles that compose the square in figure~\ref{fig:artist_heatmap} and encode that as K. We also constrain the functions on $A$, $A^\prime$, $B$ and $B^\prime$ such that $A$ can be glued to $A^\prime$ and $B$ to $B^\prime$ to reconstruct the torus.

>>>>

We use fiber bundles\cite{FiberBundle2020, rowlandFiberBundle} to model data and graphics because they allow us to seperate the variables in a dataset from how the values  are connected to each other \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre} unless otherwise specified.

@@

\subsubsection{Connectivity: Base Space $K$} 
\label{sec:data_base}
The fiber provides the schema of the dataset, but the fiber bundle is what glues that schema to a structure. The fiber bundle is the map $\pi$ between the fiber space included in the total space $E$ and the base space $K$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi"] & K
    \end{tikzcd}
\end{equation}

@@

Formally $K$ is the quotient space \cite{QuotientSpaceTopology2020} of $E$, meaning it is the finest space such that every $k \in K$ has a corresponding fiber $F_k$ in $E$. In figure~\ref{fig:base_space_div}, $E$ is a rectangle divided by vertical fibers $F$, so the minimal $K$ for which there is always a mapping $\pi: F\rightarrow K$ is the line.

@@

\subsubsection{Sample Qs}
%rewrite as alpha/beta 
In this section we formulate the minimal Q that will generate distinguishable graphical marks: non-overlapping scatter points, a non-infinitely thin line, and a simple heatmap.

@@

By using simplicies, we can then encode the following indexing structure on $\tau$
\begin{align*}
    \textbf{vertexes}\;& \tau(k) \text{k= vertex id}\\
    \textbf{edges}\;& \tau(k,\alpha), \text{k = edge id, $\alpha$ = distance along edge} \\
    \textbf{faces}\;& \tau(k,\alpha, \beta), \text{k = face id, $\alpha$ = x on face, $\beta$ = y on face}
\end{align*}

which $\xi$ can use as part of its mapping from visual space back to data space. Path connected components are then sections where $\tau(k_{i},1) = \tau(k_{j},0)$ or the edges of the faces align.

\subparagraph{Example}
\begin{figure}[ht!]
    \label{fig:triangle_torus}
    \includegraphics[width=\textwidth]{figures/math/triangle_torus.png}
    \caption{Representation of the base space $K$ of a toridal total space $E$ as two connected 2-simplices.}
\end{figure}

Given data that lies on the toroidal space shown in figure~\ref{fig:triangle_torus}, the torus $E$ base space $K$ can be implemented as a simplacial complex of two 2-simplexes. We unfold the torus into the two triangles that compose the square; the sections on these triangles are $\tau(triangle id k, \alpha, \beta)$. We also put transition functions on the edges such that $A$ can be glued to $A^\prime$ and $B$ to $B^\prime$ to reconstruct the torus.
